Particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2025-11-17 AvdMomZvolA_examples/ips_examples.tex
[AMZA] Remove technical remark
[AMZA] The information about authors

%% Прекрасно понимаю, что следующая команда - дичь и вордописчество, но время не ждёт, время жмёт
\author{
	Avdeev N.N.
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru}
	, Momot E.A., Zvolinskiy A.E.
	\\
	\\
	\emph{Voronezh State University}
}

@@

>>>>

\author{
	Avdeev N.N.
	\footnote{nickkolok@mail.ru, avdeev@math.vsu.ru}
	, Momot E.A., Zvolinskiy A.E.
	\\
	\\
	\emph{Voronezh State University}
}

@@

Авдеев Николай Николаевич

Воронежский государственный университет, кафедра теории функций и геометрии, аспирант

Россия, 394006, г. Воронеж, Университетская пл., 1

E-mail: nickkolok@mail.ru, avdeev@math.vsu.ru

Avdeev Nikolai Nikolaevich

Voronezh State University, Department of Function Theory and Geometry, postgraduate student

Russia, 394006, Voronezh, University sq., 1

Момот Екатерина Александровна

Воронежский государственный университет, кафедра функционального анализа и операторных уравнений, выпускница

Россия, 394006, г. Воронеж, Университетская пл., 1

Momot Ekaterina Alexandrovna

Voronezh State University, Department of Functional Analysis and Operator Equations, graduated from

Russia, 394006, Voronezh, University sq., 1

Зволинский Александр Евгеньевич

Воронежский государственный университет, кафедра теории функций и геометрии, выпускник

Россия, 394006, г. Воронеж, Университетская пл., 1

Zvolinsky Alexandr Evgenievich

Voronezh State University, Department of Function Theory and Geometry, graduated from

Russia, 394006, Voronezh, University sq., 1
